### 2018-07-30 Sections/cryptowars.tex
Fix document structure hierarchy

\section{CryptoWars\texttrademark\,-- Quantum cryptography}\index{Quantum key distribution}\index{Quantum cryptography}\index{CryptoWars}\label{sec:cryptowars}

@@

\subsection{What is security?}\index{Computational security}\index{Information-theoretic security}\label{sec:comp_vs_inf_th_sec}

Before describing any specific cryptographic protocols, let us define what is meant by `security' in a cryptographic context. We differentiate between \textit{information theoretic security}\index{Information-theoretic security}, as opposed to \textit{computational security}\index{Computational security}.

@@

\subsection{Classical cryptography}\index{Classical cryptography}

We begin with an introduction into \textit{classical} cryptography, so as to understand its limitations, which logically leads us into how quantum mechanics can assist in overcoming these limitations. We only scratch the surface of these extremely well-researched field, reviewing some of the most important and widely used protocols. For a deeper understanding of classical cryptography we refer the interested reader to \cite{bib:Schneier96}.

@@

\subsubsection{Private-key cryptography}\index{Private-key cryptography}

@@

\subsubsection{One-time pad cipher}\index{One-time pad cipher}

@@

\subsubsection{Public-key cryptography}\index{Public-key cryptography}

@@

\subsubsection{Key exchange protocols}

@@

\subsubsection{Digital signatures} \label{sec:dig_sig} \index{Digital signatures}

@@

\subsubsection{Hashing} \label{sec:hashing} \index{Hash functions}

@@

\subsection{Attacks on classical cryptography}\index{Cryptographic attacks}\label{sec:attacks_on_class}

@@

\subsubsection{Classical attacks}

@@

\paragraph{Brute-force}\index{Brute-force attacks}\label{sec:brute_force_attack}

@@

@@

@@

\subsection{Bitcoin \& the Blockchain}\index{Blockchain}\index{Bitcoin}\label{sec:bitcoin_blockchain}

One of the most exciting new cryptographic applications that has emerged in recent years is the Blockchain, a secure distributed ledger\index{Distributed ledger} for recording the execution of contracts and transactions. This has enabled cryptocurrencies\index{Cryptocurrencies}, most notably Bitcoin, to emerge as a secure digital alternative to conventional fiat currencies.

@@

\subsection{The end of classical cryptography?} \label{sec:end_of_class_crypto}

The vulnerability of RSA to attacks by quantum computers raises the question whether this spells the end of classical cryptography and compromises the security of much of the present-day internet.

@@

\subsection{Quantum cryptography}\index{Quantum cryptography}

@@

\subsubsection{Quantum key distribution} \label{sec:QKD} \index{Quantum key distribution}

@@

\paragraph{BB84 protocol}\index{BB84 protocol}

@@

\paragraph{Privacy amplification}\index{Privacy amplification}

@@

\paragraph{E91 protocol}\index{E91 protocol}

@@

\paragraph{Continuous-variable protocols}\index{Continuous-variable QKD}

@@

\paragraph{Security}\index{Security of QKD}

@@

\subsubsection{Hybrid quantum/classical cryptography}\index{Hybrid quantum/classical cryptography}

@@

\subsubsection{Quantum anonymous broadcasting} \label{sec:anon_broad} \index{Quantum anonymous broadcasting}

@@

\subsection{Attacks on quantum cryptography}

>>>>

@@

\section{What is security?}\index{Computational security}\index{Information-theoretic security}\label{sec:comp_vs_inf_th_sec}

\dropcap{B}{efore} describing any specific cryptographic protocols, let us define what is meant by `security' in a cryptographic context. We differentiate between \textit{information theoretic security}\index{Information-theoretic security}, as opposed to \textit{computational security}\index{Computational security}.

@@

\section{Classical cryptography}\index{Classical cryptography}

\dropcap{W}{e} begin with an introduction into \textit{classical} cryptography, so as to understand its limitations, which logically leads us into how quantum mechanics can assist in overcoming these limitations. We only scratch the surface of these extremely well-researched field, reviewing some of the most important and widely used protocols. For a deeper understanding of classical cryptography we refer the interested reader to \cite{bib:Schneier96}.

@@

\subsection{Private-key cryptography}\index{Private-key cryptography}

@@

\subsection{One-time pad cipher}\index{One-time pad cipher}

@@

\subsection{Public-key cryptography}\index{Public-key cryptography}

@@

\subsection{Key exchange protocols}

@@

\subsection{Digital signatures} \label{sec:dig_sig} \index{Digital signatures}

@@

\subsection{Hashing} \label{sec:hashing} \index{Hash functions}

@@

\section{Attacks on classical cryptography}\index{Cryptographic attacks}\label{sec:attacks_on_class}

@@

\subsection{Classical attacks}

@@

\subsection{Brute-force}\index{Brute-force attacks}\label{sec:brute_force_attack}

@@

\subsubsection{Cryptanalysis}\index{Cryptanalysis}

@@

\subsubsection{Integer factorisation}\index{Integer factorisation}

@@

\section{Bitcoin \& the Blockchain}\index{Blockchain}\index{Bitcoin}\label{sec:bitcoin_blockchain}

\dropcap{O}{ne} of the most exciting new cryptographic applications that has emerged in recent years is the Blockchain, a secure distributed ledger\index{Distributed ledger} for recording the execution of contracts and transactions. This has enabled cryptocurrencies\index{Cryptocurrencies}, most notably Bitcoin, to emerge as a secure digital alternative to conventional fiat currencies.

@@

\section{The end of classical cryptography?} \label{sec:end_of_class_crypto}

\dropcap{T}{he} vulnerability of RSA to attacks by quantum computers raises the question whether this spells the end of classical cryptography and compromises the security of much of the present-day internet.

@@

\section{Quantum cryptography}\index{Quantum cryptography}

@@

\subsection{Quantum key distribution} \label{sec:QKD} \index{Quantum key distribution}

@@

\subsubsection{BB84 protocol}\index{BB84 protocol}

@@

\subsubsection{Privacy amplification}\index{Privacy amplification}

@@

\subsubsection{E91 protocol}\index{E91 protocol}

@@

\subsubsection{Continuous-variable protocols}\index{Continuous-variable QKD}

@@

\subsubsection{Security}\index{Security of QKD}

@@

\subsection{Hybrid quantum/classical cryptography}\index{Hybrid quantum/classical cryptography}

@@

\subsection{Quantum anonymous broadcasting} \label{sec:anon_broad} \index{Quantum anonymous broadcasting}

@@

\section{Attacks on quantum cryptography}

### 2018-07-30 Sections/economics_of_the_quantum_internet.tex
Fix document structure hierarchy

\section{The economics \& politics of the quantum internet} \index{Economics}

@@

\subsection{Classical-equivalent computational power \& computational scaling functions}\index{Classical-equivalent computational power}\index{Computational scaling functions}

Let $t$ be the classical-equivalent runtime\index{Classical-equivalent computational power} of a quantum algorithm comprising $n$ qubits -- that is, how long would a given classical computer require to implement this $n$-qubit quantum computation? We define a \textit{computational scaling function}\index{Computational scaling functions} characterising this relationship,

@@

\subsubsection{Virtual computational scaling functions}\index{Virtual computational scaling functions}

@@

\subsubsection{Combined computational scaling functions}\index{Combined computational scaling functions}\label{sec:comb_comp_sc_func}

@@

\subsection{Network price scaling factor}\label{sec:NPSF}\index{Network price scaling factor}

One parameter that appears ubiquitously in the upcoming economic models and warrants a definition of its own is the computational power of a quantum computer per qubit. This relates the power and size of the computer. We define this as the \textit{network price scaling factor},

@@

\subsection{Time-sharing}\label{sec:time_share}\index{Time-sharing}

Suppose Alice and Bob both possessed expensive classical Cray\texttrademark\,supercomputers\index{Supercomputers}, both identical. They're both connected to the internet, so does it make sense to unify their computational resources over the network to construct a more powerful virtual machine\index{Virtual quantum computer}, which they subsequently time-share\index{Time-sharing} between themselves, or are they better off just using their own computers independently?

@@

\subsection{Economic model assumptions}

Before proceeding with explicit derivations of economic models, we state some assumptions about the dynamics of a marketplace in quantum assets. These assumptions are largely based on historical observations surrounding classical technologies that we might reasonably expect to also apply in the quantum era. However, given that the quantum marketplace is one that hasn't been explored in detail until now, it may be the case that some of these assumptions will require revision. Nonetheless, the general techniques we employ could readily be adapted to some relaxations and variations in these assumptions.

@@

\subsubsection{Efficient markets}\label{sec:eff_markets} \index{Efficient markets}

@@

\subsubsection{Central mediating authority}\index{Central mediating authority}

@@

\subsubsection{Network growth} \index{Network growth}

@@

\subsubsection{Hardware cost} \index{Hardware cost}

@@

\subsection{Network power}\index{Network power}\label{sec:network_power}

First and foremost, with a fully interconnected quantum computational network, what is the projection of its net computational power now and into the future? This is simply obtained via the joint computational scaling function applied to projected network size,

@@

\subsection{Network value}\index{Network value}\label{sec:network_value}

The simplest economic metric one might define is the collective dollar value of the entire network. That is, the product of the number of qubits on the network and the dollar cost per physical qubit at a given time.

@@

\subsection{Rate of return}\index{Rate of return}

The execution of computations typically has monetary value to the consumer. After all, they are paying hard-earned money for access to the technology!

@@

\subsection{Cost of computation}\label{sec:cost_of_comp} \index{Cost of computation}

In the same scenario as before, where compute-time is being licensed out to end-users, the hardware owners return over a single unit of time equates to the cost of computation over that period.

@@

\subsection{Arbitrage-free time-sharing model}\label{sec:arb_free_time_share} \index{Arbitrage-free time-sharing model}\index{Time-sharing}

In the context of our time-shared global network of unified quantum computers (Sec.~\ref{sec:time_share}), how do we fairly and equitably allocate time-shares between contributors? We now derive an elementary arbitrage-free model for equitable time-sharing in such a network.

@@

\subsection{Problem size scaling functions}\index{Problem size scaling functions}\label{sec:prob_sc_func}

The computational scaling function\index{Computational scaling functions} introduced previously expresses the power of a quantum computer in terms of its classical-equivalent runtime, or equivalently FLOPs\index{FLOPs}. However, this may not be the metric of interest when considering a computer's algorithmic power. In many situations, of far greater interest is the size of a problem\index{Problem size} instance that can be solved in a given timespan. For example, the FLOPs associated with solving an instance of a 3-\textsc{SAT} problem\index{3-SAT problem} grows exponentially with the number of clauses. When discussing the execution of this problem on a given computer, what we really want to know is how many clauses our device can cope with, rather than what the classical-equivalent runtime is.

@@

\subsection{Quantum computational leverage}\label{sec:quant_ec_lev}\index{Quantum computational leverage}

In Secs.~\ref{sec:dist_QC} \& \ref{sec:module} we introduced distributed and modularised quantum computation. Using this as a toy model, we will now investigate the market dynamics of uniting the quantum computational resources of multiple market participants, as per an equitable time-sharing model (Sec.~\ref{sec:time_share}). We envisage a model whereby network participants are contributing modules to the networked quantum computer, thereby unifying their computational power.

@@

\subsection{Forward contract pricing model}\label{sec:for_contr}\index{Forward contract pricing model}

Forward contracts are immensely useful in conventional markets, as a means by which to secure future use or ownership of an asset at predictable points in time. For example, farmers make heavy use of forward contracts to lock in sale of their produce before it has been harvested, such that the value is locked in in advance and the sale guaranteed, providing a very valuable hedging instrument\index{Hedging} for managing risk\index{Risk management}.

@@

\subsection{Economic implications}

@@

\subsubsection{The price to pay for isolationism}

@@

\subsubsection{Taxation}\label{sec:taxation}\index{Taxation}

@@

\subsubsection{Regulatory frameworks} \index{Regulatory frameworks}

@@

\subsubsection{The quantum stock market}\index{Quantum stock market}

@@

\subsection{Political leverage}\index{Political leverage}\label{sec:political_lev}

The asymmetry in computational leverage observed by parties of different sizes -- specifically, that parties possessing a smaller number of qubits observe greater leverage than those possessing a larger number of qubits -- inevitably will bring with it some power politics, with potentially interesting geo-political implications.

@@

\subsection{QuantCoin\texttrademark\,-- A quantum computation-backed cryptocurrency}\label{sec:quant_coin_technical}

As discussed in Sec.~\ref{sec:bitcoin_blockchain}, the Bitcoin\index{Bitcoin} mining\index{Mining (cryptocurrencies)} process involves finding bit-strings that hash\index{Hash functions} under SHA256\index{SHA256} to a value within some relatively small range. This so-called `proof-of-work'\index{Proof-of-work} principle associates computational complexity with the mining process, and since the hashing functions are one-way functions, they must be evaluated via brute-force trial-and-error to find hits.

@@

\subsubsection{Spot market model}\index{Spot market}

@@

\subsubsection{Futures market model}

@@

\subsection{Summary of economic models}

In Table.~\ref{tab:summary_ec_models} we summarise the economic models and parameters we developed, and applied them to several illustrative scaling functions of particular interest: linear, polynomial, and exponential.

>>>>

@@

\section{Classical-equivalent computational power \& computational scaling functions}\index{Classical-equivalent computational power}\index{Computational scaling functions}

\dropcap{L}{et} $t$ be the classical-equivalent runtime\index{Classical-equivalent computational power} of a quantum algorithm comprising $n$ qubits -- that is, how long would a given classical computer require to implement this $n$-qubit quantum computation? We define a \textit{computational scaling function}\index{Computational scaling functions} characterising this relationship,

@@

\subsection{Virtual computational scaling functions}\index{Virtual computational scaling functions}

@@

\subsection{Combined computational scaling functions}\index{Combined computational scaling functions}\label{sec:comb_comp_sc_func}

@@

\section{Network price scaling factor}\label{sec:NPSF}\index{Network price scaling factor}

\dropcap{O}{ne} parameter that appears ubiquitously in the upcoming economic models and warrants a definition of its own is the computational power of a quantum computer per qubit. This relates the power and size of the computer. We define this as the \textit{network price scaling factor},

@@

\section{Time-sharing}\label{sec:time_share}\index{Time-sharing}

\dropcap{S}{uppose} Alice and Bob both possessed expensive classical Cray\texttrademark\,supercomputers\index{Supercomputers}, both identical. They're both connected to the internet, so does it make sense to unify their computational resources over the network to construct a more powerful virtual machine\index{Virtual quantum computer}, which they subsequently time-share\index{Time-sharing} between themselves, or are they better off just using their own computers independently?

@@

\section{Economic model assumptions}

\dropcap{B}{efore} proceeding with explicit derivations of economic models, we state some assumptions about the dynamics of a marketplace in quantum assets. These assumptions are largely based on historical observations surrounding classical technologies that we might reasonably expect to also apply in the quantum era. However, given that the quantum marketplace is one that hasn't been explored in detail until now, it may be the case that some of these assumptions will require revision. Nonetheless, the general techniques we employ could readily be adapted to some relaxations and variations in these assumptions.

@@

\subsection{Efficient markets}\label{sec:eff_markets} \index{Efficient markets}

@@

\subsection{Central mediating authority}\index{Central mediating authority}

@@

\subsection{Network growth} \index{Network growth}

@@

\subsection{Hardware cost} \index{Hardware cost}

@@

\section{Network power}\index{Network power}\label{sec:network_power}

\dropcap{F}{irst} and foremost, with a fully interconnected quantum computational network, what is the projection of its net computational power now and into the future? This is simply obtained via the joint computational scaling function applied to projected network size,

@@

\section{Network value}\index{Network value}\label{sec:network_value}

\dropcap{T}{he} simplest economic metric one might define is the collective dollar value of the entire network. That is, the product of the number of qubits on the network and the dollar cost per physical qubit at a given time.

@@

\section{Rate of return}\index{Rate of return}

\dropcap{T}{he} execution of computations typically has monetary value to the consumer. After all, they are paying hard-earned money for access to the technology!

@@

\section{Cost of computation}\label{sec:cost_of_comp} \index{Cost of computation}

\dropcap{I}{n} the same scenario as before, where compute-time is being licensed out to end-users, the hardware owners return over a single unit of time equates to the cost of computation over that period.

@@

\section{Arbitrage-free time-sharing model}\label{sec:arb_free_time_share} \index{Arbitrage-free time-sharing model}\index{Time-sharing}

\dropcap{I}{n} the context of our time-shared global network of unified quantum computers (Sec.~\ref{sec:time_share}), how do we fairly and equitably allocate time-shares between contributors? We now derive an elementary arbitrage-free model for equitable time-sharing in such a network.

@@

\section{Problem size scaling functions}\index{Problem size scaling functions}\label{sec:prob_sc_func}

\dropcap{T}{he} computational scaling function\index{Computational scaling functions} introduced previously expresses the power of a quantum computer in terms of its classical-equivalent runtime, or equivalently FLOPs\index{FLOPs}. However, this may not be the metric of interest when considering a computer's algorithmic power. In many situations, of far greater interest is the size of a problem\index{Problem size} instance that can be solved in a given timespan. For example, the FLOPs associated with solving an instance of a 3-\textsc{SAT} problem\index{3-SAT problem} grows exponentially with the number of clauses. When discussing the execution of this problem on a given computer, what we really want to know is how many clauses our device can cope with, rather than what the classical-equivalent runtime is.

@@

\section{Quantum computational leverage}\label{sec:quant_ec_lev}\index{Quantum computational leverage}

\dropcap{I}{n} Secs.~\ref{sec:dist_QC} \& \ref{sec:module} we introduced distributed and modularised quantum computation. Using this as a toy model, we will now investigate the market dynamics of uniting the quantum computational resources of multiple market participants, as per an equitable time-sharing model (Sec.~\ref{sec:time_share}). We envisage a model whereby network participants are contributing modules to the networked quantum computer, thereby unifying their computational power.

@@

\section{Forward contract pricing model}\label{sec:for_contr}\index{Forward contract pricing model}

\dropcap{F}{orward} contracts are immensely useful in conventional markets, as a means by which to secure future use or ownership of an asset at predictable points in time. For example, farmers make heavy use of forward contracts to lock in sale of their produce before it has been harvested, such that the value is locked in in advance and the sale guaranteed, providing a very valuable hedging instrument\index{Hedging} for managing risk\index{Risk management}.

@@

\section{Economic implications}

@@

\subsection{The price to pay for isolationism}

@@

\subsection{Taxation}\label{sec:taxation}\index{Taxation}

@@

\subsection{Regulatory frameworks} \index{Regulatory frameworks}

@@

\subsection{The quantum stock market}\index{Quantum stock market}

@@

\section{Political leverage}\index{Political leverage}\label{sec:political_lev}

\dropcap{T}{he} asymmetry in computational leverage observed by parties of different sizes -- specifically, that parties possessing a smaller number of qubits observe greater leverage than those possessing a larger number of qubits -- inevitably will bring with it some power politics, with potentially interesting geo-political implications.

@@

\section{QuantCoin\texttrademark\,-- A quantum computation-backed cryptocurrency}\label{sec:quant_coin_technical}

\dropcap{A}{s} discussed in Sec.~\ref{sec:bitcoin_blockchain}, the Bitcoin\index{Bitcoin} mining\index{Mining (cryptocurrencies)} process involves finding bit-strings that hash\index{Hash functions} under SHA256\index{SHA256} to a value within some relatively small range. This so-called `proof-of-work'\index{Proof-of-work} principle associates computational complexity with the mining process, and since the hashing functions are one-way functions, they must be evaluated via brute-force trial-and-error to find hits.

@@

\subsection{Spot market model}\index{Spot market}

@@

\subsection{Futures market model}

@@

\section{Summary of economic models}

\dropcap{I}{n} Table.~\ref{tab:summary_ec_models} we summarise the economic models and parameters we developed, and applied them to several illustrative scaling functions of particular interest: linear, polynomial, and exponential.

### 2018-07-30 Sections/protocols_for_the_quantum_internet.tex
Fix document structure hierarchy

\section{Protocols for the quantum internet} \label{sec:protocols_quant_int} \index{Protocols for quantum networks}\index{Low-level protocols}\index{High-level protocols}

@@

\subsection{State preparation} \index{State preparation}

The first step in any quantum protocol involves the preparation of some kind of quantum state. Some quantum states are easy and cheap to prepare. Others are complex and costly. Thus, the most fundamental quantum asset that a quantum network must handle is the preparation and communication of quantum states.

@@

\subsubsection{Coherent states} \label{sec:coherent_states} \index{Coherent state preparation}

@@

\subsubsection{Single-photons} \label{sec:single_phot_src} \index{Single-photon state preparation}

@@

\subsubsection{NOON states} \label{sec:NOON} \index{NOON state preparation}

@@

\subsubsection{Cluster states} \index{Cluster state preparation}

@@

\subsubsection{Greenberger-Horne-Zeilinger states} \index{Greenberger-Horne-Zeilinger (GHZ) states}\label{sec:GHZ_states}

@@

\subsubsection{Bell states} \label{sec:bell_state_res} \index{Bell state preparation}

@@

\subsubsection{Cat states} \index{Cat state preparation}

@@

\subsubsection{Squeezed states} \label{sec:squeezed} \index{Squeezed state preparation}

@@

\subsubsection{More exotic states of light}

@@

\subsubsection{Matter qubits} \index{Matter qubits}

@@

\subsection{Measurement} \index{Measurement}

As a last (and possibility also intermediate) step in any quantum protocol is the measurement of quantum states. State measurement is, in the most general context, essentially state preparation in reverse, and brings with it many of the same challenges.

@@

\subsubsection{Photo-detection} \label{sec:photo_detection} \index{Photo-detection}

@@

\paragraph{Mathematical representation}

@@

\paragraph{Avalanche photo-diodes}\index{Avalanche photo-diodes (APDs)}

@@

\paragraph{Superconducting photo-detectors}\index{Superconducting photo-detectors}

@@

\paragraph{Quantum dot photo-detectors}\index{Quantum dot photo-detectors}

@@

\paragraph{Photo-diodes}\index{Photo-diodes}

@@

\paragraph{Experimental issues}

@@

\subsubsection{Multiplexed photo-detection}\index{Multiplexed photo-detection}

@@

\subsubsection{Homodyning} \label{sec:homodyne} \index{Homodyne detection}

@@

\subsubsection{Bell state \& parity measurements} \label{sec:bell_proj} \index{Bell measurements}

@@

\subsubsection{Quantum non-demolition measurement}\index{Quantum non-demolition measurement}

@@

\subsubsection{Weak measurement}

@@

\subsection{Evolution}

The evolution of optical states represents an extremely broad category of quantum operations, including: passive linear optics; post-selected linear optics; non-linear optics; and, light-matter interactions. Clearly, the items in this list present technological challenges, inaccessible to many users.

@@

\subsubsection{Linear optics} \label{sec:LO_ev_archs} \index{Linear optics evolution}

@@

\subsubsection{Non-linear optics} \label{sec:non_lin_opt} \index{Non-linear optics}

@@

\subsubsection{Non-optical systems}

@@

\subsection{High-level protocols} \index{High-level protocols}

Building upon the aforementioned primitive protocols for quantum networking, we can construct a plethora of higher-level protocols that implement more powerful end-user applications. These high-level protocols are ubiquitous in quantum information processing and form building blocks for even more powerful architectures, such as full cloud quantum computing, to be discussed in Sec.~\ref{sec:cloud}.

@@

\subsubsection{Random number generation} \index{Random number generation}

@@

\subsubsection{Entanglement purification} \label{sec:ent_purif} \index{Entanglement purification}

@@

\subsubsection{Quantum state teleportation} \label{sec:teleport} \index{Quantum state teleportation}

@@

\subsubsection{Quantum gate teleportation} \label{sec:teleport_gate} \index{Quantum gate teleportation}

@@

\subsubsection{Entanglement swapping} \label{sec:swapping} \index{Entanglement swapping}

@@

\subsubsection{Quantum cryptography}\index{Quantum key distribution}\index{Quantum cryptography}\label{sec:QKD_prot}

One of the most widely demonstrated class of quantum protocols is the cryptographic ones. Most importantly, these protocols allow, at least in principle, provably secure communication between two parties, immune to any attack. Because these protocols are so important and thoroughly researched, we dedicate  Sec.~\ref{sec:cryptowars} entirely to this topic.

@@

\subsubsection{Superdense coding}\label{sec:superdense}\index{Superdense coding}

@@

Suppose Alice wishes to send classical information to Bob over a quantum channel. The HSW Theorem\index{HSW theorem}\cite{bib:holevo1998capacity, bib:schumacher1997sending} tells us that Alice can send information to Bob at a maximum rate of one bit per qubit. However, if Alice and Bob share Bell pairs, superdense coding allows information to be transmitted at a maximum rate of two bits per qubit.

@@

\subsubsection{Quantum metrology} \label{sec:metrology} \index{Quantum metrology}

@@

\subsubsection{Quantum state \& process tomography} \index{Quantum state tomography (QST)} \index{Quantum process tomography (QPT)}

@@

\subsubsection{Quantum clock synchronisation} \index{Quantum clock synchronisation}\label{sec:clock_sync}

>>>>

@@

\section{State preparation} \index{State preparation}

\dropcap{T}{he} first step in any quantum protocol involves the preparation of some kind of quantum state. Some quantum states are easy and cheap to prepare. Others are complex and costly. Thus, the most fundamental quantum asset that a quantum network must handle is the preparation and communication of quantum states.

@@

\subsection{Coherent states} \label{sec:coherent_states} \index{Coherent state preparation}

@@

\subsection{Single-photons} \label{sec:single_phot_src} \index{Single-photon state preparation}

@@

\subsection{NOON states} \label{sec:NOON} \index{NOON state preparation}

@@

\subsection{Cluster states} \index{Cluster state preparation}

@@

\subsection{Greenberger-Horne-Zeilinger states} \index{Greenberger-Horne-Zeilinger (GHZ) states}\label{sec:GHZ_states}

@@

\subsection{Bell states} \label{sec:bell_state_res} \index{Bell state preparation}

@@

\subsection{Cat states} \index{Cat state preparation}

@@

\subsection{Squeezed states} \label{sec:squeezed} \index{Squeezed state preparation}

@@

\subsection{More exotic states of light}

@@

\subsection{Matter qubits} \index{Matter qubits}

@@

\section{Measurement} \index{Measurement}

\dropcap{A}{s} a last (and possibility also intermediate) step in any quantum protocol is the measurement of quantum states. State measurement is, in the most general context, essentially state preparation in reverse, and brings with it many of the same challenges.

@@

\subsection{Photo-detection} \label{sec:photo_detection} \index{Photo-detection}

@@

\subsubsection{Mathematical representation}

@@

\subsubsection{Avalanche photo-diodes}\index{Avalanche photo-diodes (APDs)}

@@

\subsubsection{Superconducting photo-detectors}\index{Superconducting photo-detectors}

@@

\subsubsection{Quantum dot photo-detectors}\index{Quantum dot photo-detectors}

@@

\subsubsection{Photo-diodes}\index{Photo-diodes}

@@

\subsubsection{Experimental issues}

@@

\subsection{Multiplexed photo-detection}\index{Multiplexed photo-detection}

@@

\subsection{Homodyning} \label{sec:homodyne} \index{Homodyne detection}

@@

\subsection{Bell state \& parity measurements} \label{sec:bell_proj} \index{Bell measurements}

@@

\subsection{Quantum non-demolition measurement}\index{Quantum non-demolition measurement}

@@

\subsection{Weak measurement}

@@

\section{Evolution}

\dropcap{T}{he} evolution of optical states represents an extremely broad category of quantum operations, including: passive linear optics; post-selected linear optics; non-linear optics; and, light-matter interactions. Clearly, the items in this list present technological challenges, inaccessible to many users.

@@

\subsection{Linear optics} \label{sec:LO_ev_archs} \index{Linear optics evolution}

@@

\subsection{Non-linear optics} \label{sec:non_lin_opt} \index{Non-linear optics}

@@

\subsection{Non-optical systems}

@@

\section{High-level protocols} \index{High-level protocols}

\dropcap{B}{uilding} upon the aforementioned primitive protocols for quantum networking, we can construct a plethora of higher-level protocols that implement more powerful end-user applications. These high-level protocols are ubiquitous in quantum information processing and form building blocks for even more powerful architectures, such as full cloud quantum computing, to be discussed in Sec.~\ref{sec:cloud}.

@@

\subsection{Random number generation} \index{Random number generation}

@@

\subsection{Entanglement purification} \label{sec:ent_purif} \index{Entanglement purification}

@@

\subsection{Quantum state teleportation} \label{sec:teleport} \index{Quantum state teleportation}

@@

\subsection{Quantum gate teleportation} \label{sec:teleport_gate} \index{Quantum gate teleportation}

@@

\subsection{Entanglement swapping} \label{sec:swapping} \index{Entanglement swapping}

@@

\subsection{Quantum cryptography}\index{Quantum key distribution}\index{Quantum cryptography}\label{sec:QKD_prot}

One of the most widely demonstrated class of quantum protocols is the cryptographic ones. Most importantly, these protocols allow, at least in principle, provably secure communication between two parties, immune to any attack. Because these protocols are so important and thoroughly researched, we dedicate  Part.~\ref{part:quant_crypto} entirely to this topic.

@@

\subsection{Superdense coding}\label{sec:superdense}\index{Superdense coding}

@@

Suppose Alice wishes to send classical information to Bob over a quantum channel. The HSW Theorem\index{HSW theorem} \cite{bib:holevo1998capacity, bib:schumacher1997sending} tells us that Alice can send information to Bob at a maximum rate of one bit per qubit. However, if Alice and Bob share Bell pairs, superdense coding allows information to be transmitted at a maximum rate of two bits per qubit.

@@

\subsection{Quantum metrology} \label{sec:metrology} \index{Quantum metrology}

@@

\subsection{Quantum state \& process tomography} \index{Quantum state tomography (QST)} \index{Quantum process tomography (QPT)}

@@

\subsection{Quantum clock synchronisation} \index{Quantum clock synchronisation}\label{sec:clock_sync}
